\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-10 paper/ms.tex
Metropolis for NS

>>>>

In Nested Sampling, the target distribution is not the posterior but rather
the constrained prior. Hence, the appropriate acceptance probability is
\begin{align}
\alpha &= \min\left[1,
\frac{q(\params'|\params)}{q(\params | \params')}
\frac{\pi(\params')}{\pi(\params)}
\mathds{1}\left(L(\params') > L^*\right)
\right]
\end{align}
where $L^*$ is the threshold value of the likelihood.

The \pkg{DNest4} \code{Sampler} class handles the likelihood check,
while the \code{perturb(DNest4::RNG\&)} member function handles the
rest of the terms. The value returned from \code{perturb(DNest4::RNG\&)}
must be
$\ln\left[q(\params'|\params)/q(\params'|\params)\times\pi(\params')/\pi(\params)\right]$ for your problem.
